### 2020-05-17 paper.tex
rxjs-spy & rxviz

Where individual transformations of an RP based program can be inspected using traditional debuggers, they fall short in understanding the greater model of the dependency graph. In fact, RP provides its own challenges to debuggers: So are call stacks spoiled with invocations of RP runtime system internal matter or breakpoints can only be used on the imperative parts of transformations rather than on the data flow within the graph. Various \textbf{reactive debuggers} and visualization tools for specific RP runtimes emerged over the past few years \cite{10.1145/2884781.2884815} \cite{rxviz} \cite{10.1145/3180155.3180156} exploring this field. They have knowledge of the dependency graph and therefore allow improved interaction with RP concepts.

@@

In addition to more sophisticated logging, three subjects reported that they built a habit of decomposing complex graphs into smaller, simpler bits and running those in a dedicated environment like Rx Visualizer\footnote{\url{https://rxviz.com/}} or StackBlitz\footnote{\url{https://stackblitz.com/}}.

@@

Software engineers tend to augment their code with additional log trace statements in the situation where they have to track down a problem as we saw earlier. \emph{rxjs-spy}\footnote{\url{https://cartant.github.io/rxjs-spy/}} wants to improve on this by introducing the \mintinline{TypeScript}{tag} operator. Instead of adding log traces at debug-time, ``tagged'' \mintinline{TypeScript}{Observable}s are created right at the moment the \mintinline{TypeScript}{Observable} itself is defined. A tag as shown in Listing~\ref{lst:rxjs-spy-tag} does not influence runtime behavior at first.

@@

\subsection{RxViz}

>>>>

Where individual transformations of an RP based program can be inspected using traditional debuggers, they fall short in understanding the greater model of the dependency graph. In fact, RP provides its own challenges to debuggers: So are call stacks spoiled with invocations of RP runtime system internal matter or breakpoints can only be used on the imperative parts of transformations rather than on the data flow within the graph. Various \textbf{reactive debuggers} and visualization tools for specific RP runtimes emerged over the past few years \cite{10.1145/2884781.2884815} \cite{10.1145/3180155.3180156} \cite{rxviz} exploring this field. They have knowledge of the dependency graph and therefore allow improved interaction with RP concepts.

@@

In addition to more sophisticated logging, three subjects reported that they built a habit of decomposing complex graphs into smaller, simpler bits and running those in a dedicated environment like Rx Visualizer\cite{rxviz} or StackBlitz\footnote{\url{https://stackblitz.com/}}.

@@

Software engineers tend to augment their code with additional log trace statements in the situation where they have to track down a problem as we saw earlier. \emph{rxjs-spy}\cite{rxjsspy} wants to improve on this by introducing the \mintinline{TypeScript}{tag} operator. Instead of adding log traces at debug-time, ``tagged'' \mintinline{TypeScript}{Observable}s are created right at the moment the \mintinline{TypeScript}{Observable} itself is defined. A tag as shown in Listing~\ref{lst:rxjs-spy-tag} does not influence runtime behavior at first.

@@

\subsection{Rx Vizualizer}

The \emph{Rx Visualizer}\cite{rxviz} is a utility available online in the browser. It is an ``animated playground for Rx Observables''\cite{rxviz} and allows to visualize snippets of RxJS code using marble diagrams.
